Online Laterality Battery Pre-Processing - short version

### 2020-11-18 battery-preprocessing_v6_DB_split2.Rmd
split half

## Updates

@@

# now merge sightedness and allsum
allsum <- merge(allsum, sightedness, by= "subject")
head(allsum) #just to check all looking OK
```

@@

# now create a data frame only for index 
lexTALE <- select(lexTale_score, "subject", "lexTALE")
# now merge with allsum
allsum <- merge(allsum, lexTALE, by= "subject")
# now write the full allsum 
write.csv(allsum, file = "./allsum_out.csv")

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "https://osf.io/mhk29/download" #day 1 data

  if (d ==2){
    data_file <-  "https://osf.io/ebm6s/download"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

all_dat2$word_OG<-NA #create dummy column just to make it easier to align columns
collist <- colnames(all_dat1)
all_dat2 <- all_dat2[,collist]
```

@@

```{r makesubject}
#Use allsum as the basis for the check
#First rename all subject to origID
allsum <- allsum %>% rename(origID = subject) 
all_dat1 <- all_dat1 %>% rename(origID = subject) 
all_dat2 <- all_dat2 %>% rename(origID = subject) 
all_dat1$subject <- NA
all_dat2$subject <- NA
for (n in 1:nrow(allsum)){
  allsum$subject[n] <- n
  w<-which(all_dat1$origID == allsum$origID[n])
  all_dat1$subject[w] <-n
  w<-which(all_dat2$origID == allsum$origID[n])
  all_dat2$subject[w] <-n
}
head(allsum)
```

@@

```{r maketaskdataframe, warning=FALSE}
make.df <- function(origdat,varlist,latlist,nloop){
nsub<-length(unique(origdat$subject))
# create compact data frame ; one row for each subject, subjects stacked, L above R
temp_dat <- data.frame(matrix(ncol = 4, nrow = nsub*nloop))
colnames(temp_dat) <- varlist
myrow <- 0 # start row counter
for (i in 1:nsub) { # loop through subjects
  subname <- i # find subject 
  myrows <- which(origdat$subject==subname) # select rows for this subject
  latcol <- which(colnames(origdat) == varlist[2])
  RTcol <- which(colnames(origdat) == varlist[4])
  tmp <- data.frame(origdat[myrows,]) #all trials from this subject

@@

# now create a data frame for lat index 
Lsubjectf <- select(Lsubjectf, "subject", "LI")
# now merge with allsum
# First check if this column already exists and delete it if so
w<-which(colnames(allsum)==mycolname)
if(length(w)>0){
allsum<-allsum[,-w]}

@@

# now create a data frame for lat index 
Zdf <- select(Zdf, "subject", "Z")
# now merge with allsum
# First check if this column already exists and delete it if so
w<-which(colnames(allsum)==mycolname)
if(length(w)>0){
allsum<-allsum[,-w]} #delete cols that already exist with that name

@@

```{r read_face_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_dat1
  if (d==2)
  {origfile <- all_dat2}
#As with earlier reading in, we default to saving CF_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Chimeric faces"
wanted <- c("subject", "stimuli", "Response", "RT", "l_hemiface", "r_hemiface","Correct") # select wanted columns - nb added Correct here
disp <- "e_Task"
CF_dat_all <- procdata(origfile,wanted,task,disp) #use generic function (see above) to read in relevant columns

@@

```{r excludelowCFacc}
#db modified to mark rather than drop cases with scores < .75
allsum$exclude <- 0 #default is to exclude

# mark the cases where there is less than 75% for identical stimuli
w <- union(which(allsum$Emot.corr.same1 < .75),which(allsum$Emot.corr.same2 < .75))
allsum$exclude[w]<-1 #code exclude = 1 if excluded because poor emot recog
print(paste('N flagged for exclusion because < 75% on at least one trial:',length(w)))

@@

#First look at accuracy, Day 1
origdat <- chim_dat1[(chim_dat1$subject %in% inclsubs),]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc with the dopirate function
task <- 'Chimeric faces day 1'
dopirate(origdat,task,measure)
#Same function will do RT next
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2
#-------------------------
#We need to add a step to exclude accuracy and RT if fewer than 3 trials in one condition. This only affects 2nd session data, so this code is specific to that file
w<-which(chim_dat2$N<2)
dropsub <- chim_dat2$subject[w]
chim_dat2$accurate[chim_dat2$subject %in% dropsub]<-NA
chim_dat2$RT[chim_dat2$subject %in% dropsub]<-NA
#-------------------------
origdat <- chim_dat2[(chim_dat2$subject %in% inclsubs),]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Chimeric faces day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)

@@

#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
chimdatL1<-select(filter(chim_dat1,side=='Left'),subject,accurate)
chimdatR1<-select(filter(chim_dat1,side=='Right'),subject,accurate)
chimdatL2<-select(filter(chim_dat2,side=='Left'),subject,accurate)
chimdatR2<-select(filter(chim_dat2,side=='Right'),subject,accurate)

allsum <- merge(allsum,chimdatL1,by="subject")
allsum <- merge(allsum,chimdatR1,by="subject")
allsum <- merge(allsum,chimdatL2,by="subject")
allsum <- merge(allsum,chimdatR2,by="subject")
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('CF1.Lraw','CF1.Rraw','CF2.Lraw','CF2.Rraw')

@@

```{r read_dichotic_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_dat1
  if (d==2)
  {origfile <- all_dat2}
# lowercase for responses
origfile$left_channel <- tolower(origfile$left_channel)
origfile$right_channel <- tolower(origfile$right_channel)
# make meaningful stimuli name
origfile$stimuli <- paste0(origfile$left_channel, "-", origfile$right_channel)
#As with earlier reading in, we default to saving dichotic_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Dichotic Listening"
wanted <- c("subject", "stimuli", "Response", "RT", "left_channel", "right_channel") # select wanted columns
disp <- "e_task"
dichotic_all <- procdata(origfile,wanted,task,disp) #use generic function (see above) to read in relevant columns

@@

```{r dosummarydich}
includesubs <- which(allsum$exclude<2) #only plot/t-test included cases
origdat <- DL_dat1[DL_dat1$subject %in% includesubs,]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 1'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2
origdat <-  DL_dat2[DL_dat2$subject %in% includesubs,]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
```
```{r add.dichotic.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
DLdatL1<-select(filter(DL_dat1,side=='Left'),subject,accurate)
DLdatR1<-select(filter(DL_dat1,side=='Right'),subject,accurate)
DLdatL2<-select(filter(DL_dat2,side=='Left'),subject,accurate)
DLdatR2<-select(filter(DL_dat2,side=='Right'),subject,accurate)

#Add to allsum
allsum <- merge(allsum,DLdatL1,by="subject")
allsum <- merge(allsum,DLdatR1,by="subject")
allsum <- merge(allsum,DLdatL2,by="subject")
allsum <- merge(allsum,DLdatR2,by="subject")
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('DL1.Lraw','DL1.Rraw','DL2.Lraw','DL2.Rraw')
#remove cases with technical errors from session 2
allsum$DL2.Lraw[techerr]<-NA
allsum$DL2.Rraw[techerr]<-NA

@@

  origfile <- all_dat1
  if(d==2)
  {origfile <- all_dat2}
  task <- "Rhyme Detection Task"
  disp <- "Task"

@@

```{r makedf_rhyme}
#We create RDT files for day1 and day 2
varlist <-   c("subject", "side", "accurate", "RT") #need to be in this order, ie sub, side, acc and RR
latlist <- c("left","no rhyme","right") #names of factor levels
nloop<-length(latlist)
RDT_df1 <- make.df(RDT_dat1,varlist,latlist,nloop)
RDT_df2 <- make.df(RDT_dat2,varlist,latlist,nloop)

@@

#Also record % correct for each category in allsum
for (d in 1:2){
  myfile<-RDT_df1
  if(d==2){ myfile<-RDT_df2}
pcorL<-myfile[myfile$side=='left',]
pcorR<- myfile[myfile$side=='right',]
pcorNull <- myfile[myfile$side=='no rhyme',]
pcorL<-select(pcorL,subject,p.corr)
pcorR<-select(pcorR,subject,p.corr)
pcorNull<-select(pcorNull,subject,p.corr)
colnames(pcorL)[2]<-paste0('RDT',d,'.pcorrL')
colnames(pcorR)[2]<-paste0('RDT',d,'.pcorrR')
colnames(pcorNull)[2]<-paste0('RDT',d,'.pcorrNull')
allsum <- merge(allsum,pcorL,by="subject")
allsum <- merge(allsum,pcorR,by="subject")
allsum <- merge(allsum,pcorNull,by="subject")
}

@@

```{r RDT_exclude}
wn <-unique(which(RDT_df1$accurate ==0),which(RDT_df2$accurate ==0)) #this catches those who were always wrong on 'no rhyme' trials, and possibly others where presentation messed up for technical reasons

@@

exRDT<-unique(c(RDT_df1$subject[w1],RDT_df2$subject[w2],RDT_df2$subject[wn]))

@@

@@

```{r add.rdt.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
RDTdatL1<-select(filter(RDT_df1,side=='left'),subject,RT)
RDTdatR1<-select(filter(RDT_df1,side=='right'),subject,RT)
RDTdatL2<-select(filter(RDT_df2,side=='left'),subject,RT)
RDTdatR2<-select(filter(RDT_df2,side=='right'),subject,RT)

allsum <- merge(allsum,RDTdatL1,by="subject")
allsum <- merge(allsum,RDTdatR1,by="subject")
allsum <- merge(allsum,RDTdatL2,by="subject")
allsum <- merge(allsum,RDTdatR2,by="subject")
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('RDTlog1.Lraw','RDTlog1.Rraw','RDTlog2.Lraw','RDTlog2.Rraw')

@@

# accuracy
origdat$X1 <- origdat$p.corr
origdat$side <- as.factor(origdat$side)
levels(origdat$side) <-c('Left','No rhyme','Right') #function assumes capitalised
mycolname<-"Day1.RDT_p.corr_LI"
if(d==2){mycolname<-"Day2.RDT_p.corr_LI"}
polarity<- (-1) #so LI is positive in predicted direction
mycutoff <- 75
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)

@@

  for (i in 1:nsubs) {
    mysub<-filter(myfile,side %in% c('left','right'),subject==allsum$subject[i])
    if(nrow(mysub)>10)
    {
      myt<-t.test(mysub$RT~mysub$side) #this is based on logRT
      allsum$tempt[i]<-myt$statistic
    }
  }
  wc<-which(colnames(allsum)=='tempt')
  colnames(allsum)[wc]<-paste0('tlat_RDT_',d)

@@

w<-which(is.na(allsum$Day1.RDT_RT_LI)) #remove those with NA in LI
allsum$tlat_RDT_1[w]<-NA
w<-which(is.na(allsum$Day2.RDT_RT_LI))
allsum$tlat_RDT_2[w]<-NA

@@

plot(allsum$Day1.RDT_RT_LI,allsum$tlat_RDT_1,xlim=c(-1.5,1.5),ylim=c(-5,5))
```

@@

#compare t-value from day 1 and day 2 
myr <- cor(allsum$zlat_RDT_1,allsum$zlat_RDT_2,use='complete.obs')
plot(allsum$zlat_RDT_1,allsum$zlat_RDT_2,xlim=c(-5,5),ylim=c(-5,5))
abline(v=0)
abline(h=0)
abline(v=-1.65,lty=2,col='red') 
abline(h=-1.65,lty=2,col='red')
abline(v=1.65,lty=2,col='red') 
abline(h=1.65,lty=2,col='red')
text(-3,3,paste0('r = ',round(myr,3)))

@@

```{r readdataFinger, warning=FALSE}
for (d in 1:2){
finger <- all_dat2[all_dat2$Task.Name=='Finger Tapping',]
if(d==1){
finger <- all_dat1[all_dat1$Task.Name=='Finger Tapping',]}
# cleaning
finger <- finger[finger$Attempt >= 1,] # only answers 
finger <- finger[finger$display == "right hand" | finger$display == "left hand",] # only for task

@@

# lets keep a running check on the participants completing here
complete.day2.FT <- unique(all_finger2$subject)
```

```{r readdataFinger2, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_finger1
  if (d==2)
  {origfile <- all_finger2}
#As with earlier reading in, we default to saving finger2 (day2), but at end of the chunk we reassign to finger1 in the first run through the d loop
finger2 <- origfile

finger2$RTbase[2:nrow(finger2)]<-finger2$RT[1:(nrow(finger2)-1)]
finger2$RTa <- finger2$RT-finger2$RTbase
#remove negative or v long RTs - can indicate when block changes etc
w<-c(which(finger2$RTa<0),which(finger2$RTa>1000))
finger2$RTa[w]<-NA
if (d==1)
{finger1 <- finger2
 }
}
```

@@

```{r scorefinger}
# We can go directly to creation of a data.frame by subjects, and use string matching to identify N correct seqs

myseq <-c('tumb','wrvx') # R, # L

@@

```{r dosummary2, warning = F}
origdat <- finger.long
measure <- '1'
origdat$X1 <- origdat$`1` #we used a dummy column name X1, so we can vary the data that are used in the pirate plot etc
task <- 'day 1'
dopirate(origdat,task,measure)

@@

```{r fingerLI}
task<-'Finger'
origdat<-finger.long
origdat$X1 <- origdat$`1`
mycolname<-"Day1_finger_LI"
mycutoff <- 10 #NB! need to check against prereg. I think this is N correct, rather than percentage. People with avg scores below this value will be excluded.
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)

>>>>

## Updates
17 Nov - changed some 'select' commands to dplyr::select
Also ensured that 'merge' selected ALL

Modified to allow rerun on split half.
For this we take blocks of 4 rows, e.g. 1,2,3,4,9,10,11,12 etc.
This way the script will work for finger tapping as well as the other tasks.
Idea is to do this selection of rows right at the outset on the raw file.

@@

# now merge sightedness and allsum
allsum <- merge(allsum, sightedness, by= "subject",all=TRUE)
head(allsum) #just to check all looking OK
```

@@

# now create a data frame only for index 
lexTALE <- dplyr::select(lexTale_score, "subject", "lexTALE")
# now merge with allsum
allsum <- merge(allsum, lexTALE, by= "subject",all=TRUE)
# now write the full allsum 
write.csv(allsum, file = "./allsum_out.csv")

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory

  data_file <- "https://osf.io/mhk29/download" #day 1 data
  all_dat1 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)

    data_file <-  "https://osf.io/ebm6s/download"
     all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)

   all_dat1$Session<-1
   all_dat2$Session<-2

     #need to align cols so can combine

      all_dat2<-all_dat2[,-1]  #extraneous first column
      all_dat1<-all_dat1[,-56] #extraneous X56 col
      all_dat2<-all_dat2[,-64] #extraneous X56 col

      alldat<-rbind(all_dat1,all_dat2[,colnames(all_dat1)])

alldat %>% filter(Attempt >= 1) # only answers 
# write as factors
alldat$subject <- as.factor(alldat$Participant.Public.ID)
alldat$RT <- as.numeric(as.character(alldat$Reaction.Time))
alldat$Trial <-as.numeric(alldat$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
alldat$Task.Name <- as.factor(alldat$Task.Name)
alldat$word<-substring(alldat$word,66,(nchar(alldat$word)-4)) #remove format from written word stimuli
oddeven <- 1 #set to zero for full dataset; to 1 for odds, and to 2 for evens
nr<-nrow(alldat)

if (oddeven==1){
  alldat<-alldat[alldat$Trial%%2==1,] #odd trials only
}
if (oddeven==2){
  alldat<-alldat[alldat$Trial%%2==0,] #even trials only
}

alldat$word_OG<-NA #create dummy column just to make it easier to align columns

@@

```{r makesubject}
#Use allsum as the basis for the check
#First rename all subject to origID
allsum <- allsum %>% rename(origID = subject) 
alldat <- alldat %>% rename(origID = subject)

alldat$subject <- NA

for (n in 1:nrow(allsum)){
  allsum$subject[n] <- n
  w<-which(alldat$origID == allsum$origID[n])
  alldat$subject[w] <-n

}
head(allsum)
```

@@

```{r maketaskdataframe, warning=FALSE}
make.df <- function(origdat,varlist,latlist,nloop){
nsub<-length(unique(origdat$subject))
# create compact data frame ; one row for each subject, subjects stacked, L above R
temp_dat <- data.frame(matrix(ncol = length(varlist), nrow = nsub*nloop))
#Previously just 4 cols but now including participant ID to check this is consistent
colnames(temp_dat) <- varlist
myrow <- 0 # start row counter
for (i in 1:nsub) { # loop through subjects
  subname <- i # find subject 
  myrows <- which(origdat$subject==subname) # select rows for this subject
  latcol <- which(colnames(origdat) == varlist[2])
  RTcol <- which(colnames(origdat) == varlist[4])
  tmp <- data.frame(origdat[myrows,]) #all trials from this subject

@@

# now create a data frame for lat index 
Lsubjectf <- dplyr::select(Lsubjectf, "subject", "LI")
# now merge with allsum
# First check if this column already exists and delete it if so
w<-which(colnames(allsum)==mycolname)
if(length(w)>0){
allsum<-allsum[,-w]}

@@

# now create a data frame for lat index 
Zdf <- dplyr::select(Zdf, "subject", "Z")
# now merge with allsum
# First check if this column already exists and delete it if so
w<-which(colnames(allsum)==mycolname)
if(length(w)>0){
allsum<-allsum[,-w]} #delete cols that already exist with that name

@@

```{r read_face_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- alldat[alldat$Session==d,]

#As with earlier reading in, we default to saving CF_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Chimeric faces"
wanted <- c("subject", "stimuli", "Response", "RT", "l_hemiface", "r_hemiface","Correct") # select wanted columns - nb added Correct here
disp <- "e_Task"
CF_dat_all <- procdata(origfile,wanted,task,disp) #use generic function (see above) to read in relevant columns

@@

```{r excludelowCFacc}
#db modified to mark rather than drop cases with scores < .75
allsum$exclude <- 0 #default is to include

# mark the cases where there is less than 75% for identical stimuli
w <- union(which(allsum$Emot.corr.same1 < .75),which(allsum$Emot.corr.same2 < .75))
allsum$exclude[w]<-1 #code exclude = 1 if excluded because poor emot recog

print(paste('N flagged for exclusion because < 75% on at least one trial:',length(w)))
w <- union(which(allsum$Emot.corr.diff1 ==0),which(allsum$Emot.corr.diff2 == 0)) #also exclude if no correct response on one side
allsum$exclude[w]<-2 #code exclude = 2 if excluded because no response one side
```

@@

#-------------------------
#We need to add a step to exclude accuracy and RT if fewer than 3 trials in one condition.

w<-which(chim_dat1$N<2)
if(length(w)>0){
dropsub <- chim_dat1$subject[w]
chim_dat1$accurate[chim_dat1$subject %in% dropsub]<-NA
chim_dat1$RT[chim_dat1$subject %in% dropsub]<-NA
}
w<-which(chim_dat2$N<2)
if(length(w)>0){
dropsub <- chim_dat2$subject[w]
chim_dat2$accurate[chim_dat2$subject %in% dropsub]<-NA
chim_dat2$RT[chim_dat2$subject %in% dropsub]<-NA
}

#First look at accuracy, Day 1
origdat <- chim_dat1[(chim_dat1$subject %in% inclsubs),]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc with the dopirate function
task <- 'Chimeric faces day 1'
dopirate(origdat,task,measure)
#Same function will do RT next
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2

#-------------------------
origdat <- chim_dat2[(chim_dat2$subject %in% inclsubs),]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Chimeric faces day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)

@@

#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
chimdatL1<-dplyr::select(filter(chim_dat1,side=='Left'),subject,accurate)
chimdatR1<-dplyr::select(filter(chim_dat1,side=='Right'),subject,accurate)
chimdatL2<-dplyr::select(filter(chim_dat2,side=='Left'),subject,accurate)
chimdatR2<-dplyr::select(filter(chim_dat2,side=='Right'),subject,accurate)

allsum <- merge(allsum,chimdatL1,by="subject",all=TRUE)
allsum <- merge(allsum,chimdatR1,by="subject",all=TRUE)
allsum <- merge(allsum,chimdatL2,by="subject",all=TRUE)
allsum <- merge(allsum,chimdatR2,by="subject",all=TRUE)
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('CF1.Lraw','CF1.Rraw','CF2.Lraw','CF2.Rraw')

@@

```{r read_dichotic_dat, warning=FALSE}
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- alldat[alldat$Session==d,]

# lowercase for responses
origfile$left_channel <- tolower(origfile$left_channel)
origfile$right_channel <- tolower(origfile$right_channel)
# make meaningful stimuli name
origfile$stimuli <- paste0(origfile$left_channel, "-", origfile$right_channel)
#As with earlier reading in, we default to saving dichotic_dat2 (day2), but at end of the chunk we reassign to CF_day1 in the first run through the d loop
task <- "Dichotic Listening"
wanted <- c("subject", "stimuli", "Response", "RT", "left_channel", "right_channel") # select wanted columns
disp <- "e_task"
dichotic_all <- procdata(origfile,wanted,task,disp) #use generic function (see above) to read in relevant columns

@@

```{r dosummarydich}
includesubs <- which(allsum$exclude<2) #only plot/t-test included cases
origdat <- DL_dat1[DL_dat1$subject %in% includesubs,]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 1'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2
origdat <-  DL_dat2[DL_dat2$subject %in% includesubs,]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
```
```{r add.dichotic.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
DLdatL1<-dplyr::select(filter(DL_dat1,side=='Left'),subject,accurate)
DLdatR1<-dplyr::select(filter(DL_dat1,side=='Right'),subject,accurate)
DLdatL2<-dplyr::select(filter(DL_dat2,side=='Left'),subject,accurate)
DLdatR2<-dplyr::select(filter(DL_dat2,side=='Right'),subject,accurate)

#Add to allsum
allsum <- merge(allsum,DLdatL1,by="subject",all=TRUE)
allsum <- merge(allsum,DLdatR1,by="subject",all=TRUE)
allsum <- merge(allsum,DLdatL2,by="subject",all=TRUE)
allsum <- merge(allsum,DLdatR2,by="subject",all=TRUE)
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('DL1.Lraw','DL1.Rraw','DL2.Lraw','DL2.Rraw')
#remove cases with technical errors from session 2
allsum$DL2.Lraw[techerr]<-NA
allsum$DL2.Rraw[techerr]<-NA

@@

  origfile <- alldat[alldat$Session==d,]

  task <- "Rhyme Detection Task"
  disp <- "Task"

@@

```{r makedf_rhyme}
#We create RDT files for day1 and day 2
varlist <-   c("subject", "side", "accurate", "RT","Participant.Public.ID") #need to be in this order, ie sub, side, acc and RR
latlist <- c("left","no rhyme","right") #names of factor levels
nloop<-length(latlist)
RDT_df1 <- make.df(RDT_dat1,varlist,latlist,nloop)
RDT_df2 <- make.df(RDT_dat2,varlist,latlist,nloop)

@@

#Also record % correct for each category in allsum
for (d in 1:2){
  myfile<-RDT_df1
  if(d==2){ myfile<-RDT_df2}
pcorL<-myfile[myfile$side=='left',]
pcorR<- myfile[myfile$side=='right',]
pcorNull <- myfile[myfile$side=='no rhyme',]
pcorL<-dplyr::select(pcorL,subject,p.corr)
pcorR<-dplyr::select(pcorR,subject,p.corr)
pcorNull<-dplyr::select(pcorNull,subject,p.corr)
colnames(pcorL)[2]<-paste0('RDT',d,'.pcorrL')
colnames(pcorR)[2]<-paste0('RDT',d,'.pcorrR')
colnames(pcorNull)[2]<-paste0('RDT',d,'.pcorrNull')
allsum <- merge(allsum,pcorL,by="subject",all=TRUE)
allsum <- merge(allsum,pcorR,by="subject",all=TRUE)
allsum <- merge(allsum,pcorNull,by="subject",all=TRUE)
}

@@

```{r RDT_exclude}

w1x<-which(is.na(RDT_df1$RT))
w2x<-which(is.na(RDT_df2$RT))

exRDTx<-unique(c(RDT_df1$subject[w1x],RDT_df2$subject[w2x]))

#find those who never got the no rhyme correct
nr1<-RDT_df1[RDT_df1$side=='no rhyme',] 
nr2<-RDT_df2[RDT_df2$side=='no rhyme',]

w1<-which(nr1$p.corr==0)
w2<-which(nr2$p.corr==0)

exRDT<-unique(c(nr1$subject[w1],nr2$subject[w2]))

wr1<-RDT_df1[RDT_df1$side!='no rhyme',] 
wr2<-RDT_df2[RDT_df2$side!='no rhyme',]

w1a<-which(wr1$p.corr<75)
w2a<-which(wr2$p.corr<75)

exRDT2<-unique(c(wr1$subject[w1a],wr2$subject[w2a]))
exRDT<-unique(c(exRDT,exRDT2))
exRDT<-sort(exRDT)

allsum$exRDT <- 0

allsum$exRDT[allsum$subject %in% exRDT]<-1 #decided best to have separate column for exclusion for each task
allsum$exRDT[allsum$subject %in% exRDTx]<-2 #missing data
w<-which(allsum$exRDT==0)  
incRDT <- allsum$subject[w]
ninc <- length(incRDT)
print(paste0('RDT: number remaining after exclusions = ',ninc))

RDT_df1<-RDT_df1[RDT_df1$subject %in% incRDT,]
RDT_df2<-RDT_df2[RDT_df2$subject %in% incRDT,]

RDT_df1<-RDT_df1[RDT_df1$side !='no rhyme',]
RDT_df2<-RDT_df2[RDT_df2$side !='no rhyme',]

```
```{r oldRDT_exclude}
#Original version now superseded
doold<-0
if(doold==1){
  wn <-unique(which(RDT_df1$accurate ==0),which(RDT_df2$accurate ==0)) #this catches those who were always wrong on 'no rhyme' trials, and possibly others where presentation messed up for technical reasons

@@

exRDT<-sort(unique(c(RDT_df1$subject[w1],RDT_df2$subject[w2],RDT_df2$subject[wn])))

@@

}
```

@@

```{r add.rdt.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
RDTdatL1<-dplyr::select(filter(RDT_df1,side=='left'),subject,RT)
RDTdatR1<-dplyr::select(filter(RDT_df1,side=='right'),subject,RT)
RDTdatL2<-dplyr::select(filter(RDT_df2,side=='left'),subject,RT)
RDTdatR2<-dplyr::select(filter(RDT_df2,side=='right'),subject,RT)

allsum <- merge(allsum,RDTdatL1,by="subject",all=TRUE)
allsum <- merge(allsum,RDTdatR1,by="subject",all=TRUE)
allsum <- merge(allsum,RDTdatL2,by="subject",all=TRUE)
allsum <- merge(allsum,RDTdatR2,by="subject",all=TRUE)
myn <-ncol(allsum)
colnames(allsum)[(myn-3):myn] <- c('RDTlog1.Lraw','RDTlog1.Rraw','RDTlog2.Lraw','RDTlog2.Rraw')

@@

# accuracy
origdat$X1 <- origdat$p.corr
origdat$side <- as.factor(origdat$side)
levels(origdat$side) <-c('Left','Right') #function assumes capitalised
mycolname<-"Day1.RDT_p.corr_LI"
if(d==2){mycolname<-"Day2.RDT_p.corr_LI"}
polarity<- (-1) #so LI is positive in predicted direction
mycutoff <- 75
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)

@@

  for (i in 1:nsubs) {
    mysub<-filter(myfile,side %in% c('left','right'),subject==allsum$subject[i])
    if(nrow(mysub)>10)
    {
      myt<-t.test(mysub$RT~mysub$side) #this is based on logRT
      allsum$tempt[i]<-myt$statistic
    }
  }
    w<-which(is.na(allsum$Day2.RDT_RT_LI)) #remove those with NA in LI
  allsum$tempt[w]<-NA
  wc<-which(colnames(allsum)=='tempt')

  colnames(allsum)[wc]<-paste0('tlat_RDT_',d)

@@

@@

plot(allsum$Day1.RDT_RT_LI,allsum$tlat_RDT_1,xlim=c(-1.5,1.5),ylim=c(-5,5))
#NB t test and LI will disagree because same size of difference will give different t depending on how much variance there is for L and R responses.
```

@@

#compare z-value from day 1 and day 2 
myr <- cor(allsum$zlat_RDT_1,allsum$zlat_RDT_2,use='complete.obs')
plot(allsum$zlat_RDT_1,allsum$zlat_RDT_2,xlim=c(-5,5),ylim=c(-5,5))
abline(v=0)
abline(h=0)
abline(v=-1.65,lty=2,col='red') 
abline(h=-1.65,lty=2,col='red')
abline(v=1.65,lty=2,col='red') 
abline(h=1.65,lty=2,col='red')
text(-3,3,paste0('r = ',round(myr,3)))

@@

```{r readdataFinger, warning=FALSE}
if(oddeven==0){ #won't work with split half
for (d in 1:2){
finger <- alldat[alldat$Task.Name=='Finger Tapping',]
finger <- finger[finger$Session==d,]
# cleaning
finger <- finger[finger$Attempt >= 1,] # only answers 
finger <- finger[finger$display == "right hand" | finger$display == "left hand",] # only for task

@@

# lets keep a running check on the participants completing here
complete.day2.FT <- unique(all_finger2$subject)
}
```

```{r readdataFinger2, warning=FALSE}
if(oddeven==0){
for (d in 1:2){ #we will process day 1 and day 2 together
  origfile <- all_finger1
  if (d==2)
  {origfile <- all_finger2}
#As with earlier reading in, we default to saving finger2 (day2), but at end of the chunk we reassign to finger1 in the first run through the d loop
finger2 <- origfile

finger2$RTbase[2:nrow(finger2)]<-finger2$RT[1:(nrow(finger2)-1)]
finger2$RTa <- finger2$RT-finger2$RTbase
#remove negative or v long RTs - can indicate when block changes etc
w<-c(which(finger2$RTa<0),which(finger2$RTa>1000))
finger2$RTa[w]<-NA
if (d==1)
{finger1 <- finger2
 }
}
}
```

@@

```{r scorefinger}
# We can go directly to creation of a data.frame by subjects, and use string matching to identify N correct seqs
if (oddeven==0){
myseq <-c('tumb','wrvx') # R, # L

@@

}
```

```{r dosummary2, warning = F}
if(oddeven==0){
origdat <- finger.long
measure <- '1'
origdat$X1 <- origdat$`1` #we used a dummy column name X1, so we can vary the data that are used in the pirate plot etc
task <- 'day 1'
dopirate(origdat,task,measure)

@@

```{r fingerLI}
if(oddeven==0){
task<-'Finger'
origdat<-finger.long
origdat$X1 <- origdat$`1`
mycolname<-"Day1_finger_LI"
mycutoff <- 10 #NB! need to check against prereg. I think this is N correct, rather than percentage. People with avg scores below this value will be excluded.
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeLI(allsum,origdat,task,mycolname,polarity,mycutoff)
